### 2022-08-13 ms/ms02_floats.tex
ENH went through figures

% full size table is table*
\begin{table*}[]
  \caption{Variants involved in 5 or more GWAS categories.}\label{tab:pleitropic_variants}
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=rrrrcp{0.6\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos. (hg38) & \bfseries Variant & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

@@

% full size table is table*
\begin{table*}[]
\caption{Pleiotropic regions involving 6 or more GWAS categories.}\label{tab:pleiotropic_regions}
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=rrrrcp{0.5\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Start (hg38) & \bfseries End (hg38) & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

@@

\begin{figure*}[]
\centering
%
\includegraphics[width=0.33\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
%
\caption{\textbf{Length distribution of pleiotropic regions.} (\textbf{a}) TODO.} \label{fig:pleiotropy_region_distribution}
\end{figure*}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{\textbf{Probability density of GWAS phenotypes, eGene or eQTL samples.} (\textbf{a}) TODO.} \label{fig:hist_gwas_egene_etissue}
\end{figure*}

@@

\caption{\textbf{Count of GWAS categories, eGenes and eTissues in pleiotropic genomic regions.} (\textbf{a,d,g}) Region 5:132,239,645-132,497,907, \textbf{b,e,h}) region 6:31,034,839-32,478,149,  and \textbf{c,g,i}) region 12:111,395,984-111,645,358} \label{fig:region_gwas_egenes_tissues}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{\textbf{Location of of variants computed as VEP consequence.} (\textbf{a}) TODO.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{\textbf{Frequency of eGenes per variant, eTissues per variant-eGene and phenotypes per variant-eGene-eTissue.} (\textbf{a}) TODO.} \label{fig:freq_gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remaptf.py/bxplt_remaptf_per_rsid_flank_0.png}
\end{subfigure}
%
\caption{\textbf{Binding of transcription factors in the region (100 kb) around pleiotropic variants.} (\textbf{a}) TODO.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

@@

\caption{\textbf{TODO.} (\textbf{a}) TODO.} \label{fig:beta}
%
\end{figure*}

@@

\caption{\textbf{Molecular mechanism of pleiotropy.} (We have observed three possible mechanisms resulting in pleiotropy. (Left) Pleiotropic variants have more eGenes. One explanation is that these variants are present in splicing regions. (Center) eGenes of pleiotropic variants are active in more eTissues, which might be explained from variants being bound by more transcription factors. (Right) eGenes/eTissues are associated with more GWAS phenotypes. This might be explained because the variants have more frequently a missense consequence.} \label{fig:beta}
%
\end{figure*}

>>>>

% full size table is table*
\begin{table*}[]
  \caption{Colocalized eQTL/GWAS variants involved in 5 or more GWAS categories.}\label{tab:pleitropic_variants}
\centering
\scriptsize
\hline
\csvreader[separator=tab,
tabular=rrrrcp{0.6\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos. (hg38) & \bfseries Variant & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_rsid_most_pleiotropic.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

@@

% full size table is table*
\begin{table*}[]
\caption{Pleiotropic regions involving 5 or more GWAS categories.}\label{tab:pleiotropic_regions}
\centering
\scriptsize
\hline
\csvreader[
separator=tab,
tabular=rrrrcp{0.5\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Start (hg38) & \bfseries End (hg38) & \bfseries Cat. ct. & \bfseries GWAS Categories\\\hline,
]{fig/tab_region_window_100000_pleio_highest.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv & \csvcolv & \csvcolvi}% specify your coloumns here
\hline
\end{table*}

@@

\begin{figure*}[]
\centering
%
\includegraphics[width=0.33\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
%
\caption{Length distribution of pleiotropic regions.} \label{fig:pleiotropy_region_distribution}
\end{figure*}

@@

\begin{figure*}[]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{Percentage of colocalized eQTL/GWAS variants with different number of GWAS categories (\textbf{a}), egenes (\textbf{b}) and etissues (\textbf{c}).} \label{fig:hist_gwas_egene_etissue}
\end{figure*}

@@

\caption{Count of GWAS categories (\textbf{a-c}), egenes (\textbf{d-f}) and etissues (\textbf{g-i}) in three pleiotropic genomic regions: \textbf{a,d,g}: 5:132,239,645-132,497,907 (5q31.1), \textbf{b,e,h}: 6:31,034,839-32,478,149 (6p21.33) and \textbf{c,g,i}: 12:111,395,984-111,645,358 (12q24.1)} \label{fig:region_gwas_egenes_tissues}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/missense_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/splice_region_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plt_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of egenes per variant (\textbf{a}), etissues per variant-egene (\textbf{b}) and GWAS categories per variant-egene-etissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}

@@

\begin{figure*}[!]
\centering
%
\begin{subfigure}[]{.33\textwidth}
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remaptf.py/bxplt_remaptf_per_rsid_flank_0.png}
\end{subfigure}
%
\caption{Binding of transcription factors in the region around pleiotropic variants (Radius 50 bp) as a function of the GWAS category count.} \label{fig:freq_tf_per_variant}
%
\end{figure*}

@@

\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS category count.} \label{fig:beta_pval}
%
\end{figure*}

@@

\caption{\textbf{Model of regulatory variant pleiotropy.} I have investigated three possible mechanisms of pleiotropy. \textbf{Left}, Pleiotropic variants have more egenes that result in more functions and more phenotypes. This might arise from an enrichment of pleiotropic variants in splicing or 3' UTR regions. \textbf{Center}, I have also found that egenes of pleiotropic variants are active in more etissues which result in more GWAS phenotypes. This might be explained from variants being bound by more transcription factors. \textbf{Left} Triplets of variant-egene-etissues are associated with more GWAS phenotypes, which directly affect the number of GWAS phenotypes. I have found that this might be explained by an enrichment of missense alleles.} \label{fig:beta}
%
\end{figure*}
